### 2013-02-14 doc/xps2013/proposal.tex
commit to merge

Since Grappa is designed for applications that have no or low locality, nearly \emph{every} memory reference is to a remote system node.  This makes the networking layer key to overall system performance.  In this section we outline the key directions we wish to take in enhancing the networking layer of the Grappa runtime system.

@@

Grappa applications are likely to use large amounts of data, 100s of terabytes to petabytes. Keeping all these data in DRAM only is unlikely to be cost effective. We will explore mechanisms that use solid-state storage as primary memory, greatly expanding the directly addressable storage at low cost.

>>>>

Since Grappa is designed for applications that have no or little locality, nearly \emph{every} memory reference is to a remote system node.  This makes the networking layer key to overall system performance.  In this section we outline the key directions we wish to take in enhancing the networking layer of the Grappa runtime system.

@@

Grappa applications are likely to use large amounts of data, 100s of terabytes to petabytes. Keeping all these data in DRAM only is unlikely to be cost effective. We will explore mechanisms that use solid-state storage as primary memory for program data, greatly expanding the directly addressable storage at low cost.
